\mytitle

### 2020-04-22 paper.tex
Small edit at the beginning of Sect 3

In this work, we argue that 
formulating WFLO using quadratic programming enables us to employ 
advanced software solutions (e.g., Gurobi optimizer) and approximate hardware developments 
(e.g., Fujitsu's digital annealer that solves quadratic problems using principles from simulated annealing). 
A benchmark study compared state of the art exact approaches from~\cite{Zhang2014} to 
approximate methods and found that the two perform in a comparable fashion, without large differences between
the attained energy~\cite{yang2019simulated}. Exact methods tend to perform slightly better
in smaller WFLO benchmarks, while simulated annealing methods dominated for larger standard WFLO benchmarks. 
This leads to the conclusion that both types of methods (exact and approximate) should be considered. 
Therefore, in this work, we introduce a unified paradigm, namely quadratic programming, that enables
both exact and approximate solutions to WFLO. Thus, 
our approach `enjoys' the best of both worlds (the exact and the approximate).

>>>>

In this work, we argue that 
formulating WFLO using quadratic programming enables us to employ 
recent advanced software solutions (e.g., Gurobi optimizer) and approximate hardware developments 
(e.g., Fujitsu's Digital Annealer).
%that solves quadratic problems using principles from simulated annealing). 
A benchmark study compared state of the art exact approaches from~\cite{Zhang2014} to 
approximate methods and found that the two perform in a comparable fashion, without large differences between
the attained energy~\cite{yang2019simulated}. Exact methods tend to perform slightly better
in smaller WFLO benchmarks, while simulated annealing methods dominated for larger standard WFLO benchmarks. 
This leads to the conclusion that both types of methods (exact and approximate) should be considered. 
Therefore, in this work, we introduce a unified paradigm, namely quadratic programming, that enables
both exact and approximate solutions to WFLO. Thus, 
our approach `enjoys' the best of both worlds (the exact and the approximate).
